---
title: "Example profile LOD plots from simulations"
author: "Frederick Boehm"
date: "4/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(qtl2pleio)
```

A reviewer asked us to provide example profile LOD plots for the simulated traits with F:ABCDEGH allele parititioning and small effect size (as in Figure 1, the power figure).




```{r setup}
load("~/Box Sync/attie/attiedo/DerivedData/probs_pmap.RData")
pm <- pmap$`17`
load("~/Box Sync/attie/attiedo/DerivedData/probs_gmap.RData")
gm <- gmap$`17`
```


We want to use run 319, for it has interlocus distance of 0.5 cM and small effect size (per the research notebook entry of Jan 4, 2018).











```{r read-results}
tr0 <- read.table("~/Box Sync/attie/qtl2pleio-manuscript-chtc/power-study/results/pvl400-run319/pvl400-run319_0.txt")
colnames(tr0) %in% names(gm)
```




```{r}  
tidyr::gather(tr0) %>%
  rename(Var2 = key, loglik = value) %>%
  mutate(Var1 = rep(unique(Var2), times = 210)) %>%
  select(3, 1, 2) %>%
  tidy_scan_pvl(pmap = gm) %>%
  plot_pvl(units = "cM")
```

```{r}
tr <- list()
for (i in 0:399){
  fn <- paste0("~/Box Sync/attie/qtl2pleio-manuscript-chtc/power-study/results/pvl400-run319/pvl400-run319_", i, ".txt")
  tr[[i+1]] <- read.table(fn)
}

```


```{r}
for (i in 0:399){
  fn <- paste0("~/Box Sync/attie/qtl2pleio-manuscript-chtc/power-study/results/pvl400-run319-profile-lod-plots/profile-lod", i, ".eps")
  tr0 <- tr[[i+1]]
  tidyr::gather(tr0) %>%
    rename(Var2 = key, loglik = value) %>%
    mutate(Var1 = rep(unique(Var2), times = 210)) %>%
    select(3, 1, 2) %>%
    tidy_scan_pvl(pmap = gm) %>%
    plot_pvl(units = "cM", linetype = rep("solid", 3))
  ggsave(fn, width = 7, height = 3.5, units = "in")
}
```


We also need to determine, from the bootstrap samples, the critical value for the test statistic.

```{r}
# bootstrap samples are run 309 for small effect size and uneven partitioning
boot <- list()
for (i in 0:15999){
  fn <- paste0("~/Box Sync/attie/qtl2pleio-manuscript-chtc/power-study/results/boot400-run309/boot400-run309_", i, ".txt")
  boot[[i+1]] <- read.table(fn)

}
boots <- do.call("c", boot) %>% unlist()
names(boots) <- NULL
quantile(boots, 0.95)
```

Now, let's get the lrts for each of the 400 analyses.

```{r}
lrt <- numeric(length = 400)
for (i in 0:399){
  fn <- paste0("~/Box Sync/attie/qtl2pleio-manuscript-chtc/power-study/results/pvl400-run319/pvl400-run319_", i, ".txt")
  lrt[i + 1] <- read.table(fn) %>%
    tidyr::gather() %>%
    rename(Var2 = key, loglik = value) %>%
    mutate(Var1 = rep(unique(Var2), times = 210)) %>%
    select(3, 1, 2) %>%
    calc_lrt_tib()
}
sum(lrt > quantile(boots, 0.95))
calc_lrt_matrix <- function(matrix){
  max(matrix) - max(diag(matrix))
}
lrt2 <- numeric(400)
for (i in 0:399){
  fn <- paste0("~/Box Sync/attie/qtl2pleio-manuscript-chtc/power-study/results/pvl400-run319/pvl400-run319_", i, ".txt")
  lrt2[i+1] <- read.table(fn) %>%
    as.matrix() %>%
    calc_lrt_matrix()
}

lrt == lrt2
```

Now, let's analyze the lrt vector by using each trait's 400 samples, rather than pooling all 160,000.

```{r}
crit <- numeric(400)
for (i in 0:399){
  start_index <- i * 400
  end_index <- (i + 1) * 400 - 1 
  crit[i + 1] <- quantile(boots[start_index:end_index], 0.95)
}
```

```{r}
tib <- tibble(lrt, crit) %>%
  mutate(indicator = lrt > crit)
sum(tib$indicator)
```

## Choosing 9 random profile lod plots and calculating their test statistics

We chose randomly nine profile lod plots for inclusion in the G3 manuscript.

```{r}
set.seed(8675309)
(sample(0:399, 9) -> plot_nums)
```



```{r}
tibble(plot_nums, lrt = lrt2[plot_nums + 1]) %>%
  arrange(lrt) %>%
  mutate(lrt10 = lrt / log(10))
```

```{r}
quantile(boots, 0.95) / log(10)

```

